Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-10-17 paper.tex
fixing figure labels
fixing table labels
Some comments

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{books_methodology}
\end{center}
\caption{Proposed methodology.}
\label{fig:count}
\end{figure*}

@@

Table \ref{table:freq} and Figure \ref{fig:count} reveal more information about the nature of the dataset. We can notice that most of 77\% of the boos investigated are categorized as VL and L with limited number of sales. On the other side, the books that achieved more than 2000 sold copies are just around 4\%. This makes the problem of identifying those two categories much harder. The new categorical feature is used to replace the old numerical Total Sales feature in the GP classification case.

@@

Precision is the ratio of the correctly classified instances as $i$ to the number of instances classified as $i$. On the other side, recall is the ratio of the correctly classified instances as $i$ to the number of actual $i$ instances . Precision and recall are given in Equation \ref{equation:precision} and \ref{equation:recall}, respectively.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{Confusion-matrix-multiclass-default}
\end{center}
\caption{Default cost matrix.}
\label{fig:count}
\end{figure*}

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performes regarding each class. Therefore, precision and recall rates are examined. \\

@@

\centerline{\includegraphics[scale=0.42]{RF}}

\caption{Performance of RF classifier over different number of trees.}
\label{fig:count}
\end{figure*}

@@

\caption{Performance of Bagging classifier over different number of iterations.}
\label{fig:count}
\end{figure*}

\begin{figure*}[ht]
\centerline{
\includegraphics[scale=0.46]{Adaboost}
}
\caption{Performance of Adaboost classifier over different number of iterations.}
\label{fig:count}
\end{figure*}

\begin{table}
\caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
 & RF  &  AdaBoost &  Bagging \tabularnewline
\hline 
 \hline $Accuracy$ & 0.741 $\pm$ 0.002 & 0.743 $\pm$ 0.0023 & 0.735 $\pm$ 0.0022 \tabularnewline 
 \hline 
 \hline $Recall_{L}$ & 0.796 $\pm$ 0.0038 & 0.793 $\pm$ 0.0038 & 0.792 $\pm$ 0.0048 \tabularnewline 
 \hline $Precision_{L}$ & 0.823 $\pm$ 0.0035 & 0.827 $\pm$ 0.0032 & 0.814 $\pm$ 0.0043 \tabularnewline 
 \hline 
 \hline $Recall_{M}$ & 0.748 $\pm$ 0.0033 & 0.75 $\pm$ 0.0029 & 0.738 $\pm$ 0.0038 \tabularnewline 
 \hline $Precision_{M}$ & 0.712 $\pm$ 0.0026 & 0.716 $\pm$ 0.0032 & 0.707 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{H}$ & 0.68 $\pm$ 0.0073 & 0.684 $\pm$ 0.0051 & 0.667 $\pm$ 0.0065 \tabularnewline 
 \hline $Precision_{H}$ & 0.666 $\pm$ 0.0037 & 0.667 $\pm$ 0.0029 & 0.663 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{VH}$ & 0.723 $\pm$ 0.0054 & 0.727 $\pm$ 0.0041 & 0.731 $\pm$ 0.0057 \tabularnewline 
 \hline $Precision_{VH}$ & 0.816 $\pm$ 0.0051 & 0.808 $\pm$ 0.0056 & 0.793 $\pm$ 0.0069 \tabularnewline 
\hline 
\end{tabular}
\label{table:basic_classifiers}
\end{table}

@@

This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), PRY142/14 (Fundaci{\'o}n P{\'u}blica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci{\'o}n), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).

>>>>

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{books_methodology}
\end{center}
\caption{Proposed methodology.}
\label{fig:methodology}
\end{figure*}
% Antonio - I like this figure, however, it seems on it that the results of the basic classifier are used as 'starting point' of the ensembles, and the results of these methods are used in the cost sensitive classification... is this correct? Otherwise, maybe we should change the design of the figure. ;D

@@

Table \ref{table:freq} and Figure \ref{fig:count} 
% Antonio - Not sure which Figure did you refer to... Maybe should they be Tables 'params_pre-sales' and 'freq'? :D
reveal more information about the nature of the dataset. We can notice that most of 77\% of the books investigated are categorized as VL and L with limited number of sales. On the other side, the books that achieved more than 2000 sold copies are just around 4\%. This makes the problem of identifying those two categories much harder. The new categorical feature is used to replace the old numerical Total Sales feature in the GP classification case.

@@

Precision is the ratio of the correctly classified instances as $i$ to the number of instances classified as $i$. On the other side, recall is the ratio of the correctly classified instances as $i$ to the number of actual $i$ instances. Precision and recall are given in Equation \ref{equation:precision} and \ref{equation:recall}, respectively.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.40]{Confusion-matrix-multiclass-default}
\end{center}
\caption{Default cost matrix.}
\label{fig:Default_cost_matrix}
\end{figure*}

@@

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined. \\

@@

\centerline{\includegraphics[scale=0.46]{RF}}

\caption{Performance of RF classifier over different number of trees.}
\label{fig:PerformanceRF}
\end{figure*}

@@

\caption{Performance of Bagging classifier over different number of iterations.}
\label{fig:PerformanceBagging}
\end{figure*}

\begin{figure*}[ht]
\centerline{
\includegraphics[scale=0.46]{Adaboost}
}
\caption{Performance of Adaboost classifier over different number of iterations.}
\label{fig:PerformanceAdaboost}
\end{figure*}

% Antonio - Just a comment about colors of the graphs. If one prints them in grey scale it cannot be distinguished for instance H and VH lines. ;)

\begin{table}
\caption{Classification results using ensemble classifiers (RF, AdaBoost and Bagging)}
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
 & RF  &  AdaBoost &  Bagging \tabularnewline
\hline 
 \hline $Accuracy$ & 0.741 $\pm$ 0.002 & 0.743 $\pm$ 0.0023 & 0.735 $\pm$ 0.0022 \tabularnewline 
 \hline 
 \hline $Recall_{L}$ & 0.796 $\pm$ 0.0038 & 0.793 $\pm$ 0.0038 & 0.792 $\pm$ 0.0048 \tabularnewline 
 \hline $Precision_{L}$ & 0.823 $\pm$ 0.0035 & 0.827 $\pm$ 0.0032 & 0.814 $\pm$ 0.0043 \tabularnewline 
 \hline 
 \hline $Recall_{M}$ & 0.748 $\pm$ 0.0033 & 0.75 $\pm$ 0.0029 & 0.738 $\pm$ 0.0038 \tabularnewline 
 \hline $Precision_{M}$ & 0.712 $\pm$ 0.0026 & 0.716 $\pm$ 0.0032 & 0.707 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{H}$ & 0.68 $\pm$ 0.0073 & 0.684 $\pm$ 0.0051 & 0.667 $\pm$ 0.0065 \tabularnewline 
 \hline $Precision_{H}$ & 0.666 $\pm$ 0.0037 & 0.667 $\pm$ 0.0029 & 0.663 $\pm$ 0.004 \tabularnewline 
 \hline 
 \hline $Recall_{VH}$ & 0.723 $\pm$ 0.0054 & 0.727 $\pm$ 0.0041 & 0.731 $\pm$ 0.0057 \tabularnewline 
 \hline $Precision_{VH}$ & 0.816 $\pm$ 0.0051 & 0.808 $\pm$ 0.0056 & 0.793 $\pm$ 0.0069 \tabularnewline 
\hline 
\end{tabular}
\label{table:ensemble_classifiers}
\end{table}

@@

This work has been supported in part by projects PreTEL (PRM Consultores - Trevenque S.L.), TIN2014-56494-C4-3-P and TEC2015-68752 (Spanish Ministry of Economy and Competitiveness and FEDER), and PROY-PP2015-06 (Plan Propio 2015, funded by the University of Granada, Spain).
